Processing of visual and non-visual naturalistic spatial information in the "parahippocampal place area"

### 2022-02-02 paper/main.tex
only capitalize first word of subsection headers
substitute preliminary with actual doi

\subsection*{Stimuli and Procedure}

@@

\subsection*{Hemodynamic Modeling}

@@

% new; PPA analysis
All fMRI data, annotations, and results are available as Datalad \citep{datalad}
datasets, published to or linked from the \emph{G-Node GIN} repository
(\href{https://doi.org/10.12751/g-node.qmevq0}{\url{doi.org/10.12751/g-node.qmevq0}}\citep{haeusler2021ppa}).
% original
Raw data of the audio-description, movie and visual localizer were originally
published on the \emph{OpenfMRI} portal
(\url{https://legacy.openfmri.org/dataset/ds000113}\citep{Hanke2014ds000113},
\url{https://legacy.openfmri.org/dataset/ds000113d}\citep{hanke2016ds000113d}).
% visual localizer
Results from the localization of higher visual areas are available as Datalad
datasets at \emph{GitHub} (
\href{https://github.com/psychoinformatics-de/studyforrest-data-visualrois}{\url{github.com/psychoinformatics-de/studyforrest-data-visualrois}}\citep{sengupta2016extensiondata}).
% raw data
The realigned participant-specific timeseries that were used in the current
analyses were derived from the raw data releases and are available as Datalad
datasets at \emph{GitHub} (
\href{https://github.com/psychoinformatics-de/studyforrest-data-aligned}{\url{github.com/psychoinformatics-de/studyforrest-data-aligned}}
\citep{hanke2016aligned}).
% cut annotation
The annotation of cuts is available at \emph{F1000Research}
(\href{https://doi.org/10.5256/f1000research.9536.d134823}{\url{doi.org/10.5256/f1000research.9536.d134823}}
\citep{haeusler2016cutdata}),
% speech annotation
the annotation of speech is available at \emph{OSF}
(\href{https://doi.org/10.17605/OSF.IO/F5J3E}{\url{doi.org/10.17605/OSF.IO/F5J3E}}
\citep{haeusler2020speechdata}).
% surface data
Participant-specific reconstructed cortical surface are available as Datalad
dataset at \emph{GitHub} (
\href{https://github.com/psychoinformatics-de/studyforrest-data-freesurfer}{\url{github.com/psychoinformatics-de/studyforrest-data-freesurfer}}
\citep{hanke2016freesurferdata}), and are also part of the original data release
on \emph{OpenfMRI}
(\url{https://legacy.openfmri.org/dataset/ds000113}\citep{Hanke2014ds000113}.

>>>>

\subsection*{Stimuli and procedure}

@@

\subsection*{Hemodynamic modeling}

@@

% new; PPA analysis
All fMRI data, annotations, and results are available as Datalad \citep{datalad}
datasets, published to or linked from the \emph{G-Node GIN} repository
(\href{https://doi.org/10.12751/g-node.7is9s6}{\url{doi.org/10.12751/g-node.qmevq0}}\citep{haeusler2021ppa}).
% original
Raw data of the audio-description, movie and visual localizer were originally
published on the \emph{OpenfMRI} portal
(\url{https://legacy.openfmri.org/dataset/ds000113}\citep{Hanke2014ds000113},
\url{https://legacy.openfmri.org/dataset/ds000113d}\citep{hanke2016ds000113d}).
% visual localizer
Results from the localization of higher visual areas are available as Datalad
datasets at \emph{GitHub} (
\href{https://github.com/psychoinformatics-de/studyforrest-data-visualrois}{\url{github.com/psychoinformatics-de/studyforrest-data-visualrois}}\citep{sengupta2016extensiondata}).
% raw data
The realigned participant-specific timeseries that were used in the current
analyses were derived from the raw data releases and are available as Datalad
datasets at \emph{GitHub} (
\href{https://github.com/psychoinformatics-de/studyforrest-data-aligned}{\url{github.com/psychoinformatics-de/studyforrest-data-aligned}}
\citep{hanke2016aligned}).
% cut annotation
The annotation of cuts is available at \emph{F1000Research}
(\href{https://doi.org/10.5256/f1000research.9536.d134823}{\url{doi.org/10.5256/f1000research.9536.d134823}}
\citep{haeusler2016cutdata}),
% speech annotation
the annotation of speech is available at \emph{OSF}
(\href{https://doi.org/10.17605/OSF.IO/F5J3E}{\url{doi.org/10.17605/OSF.IO/F5J3E}}
\citep{haeusler2020speechdata}).
% surface data
Participant-specific reconstructed cortical surface are available as Datalad
dataset at \emph{GitHub} (
\href{https://github.com/psychoinformatics-de/studyforrest-data-freesurfer}{\url{github.com/psychoinformatics-de/studyforrest-data-freesurfer}}
\citep{hanke2016freesurferdata}), and are also part of the original data release
on \emph{OpenfMRI}
(\url{https://legacy.openfmri.org/dataset/ds000113}\citep{Hanke2014ds000113}.
